\documentclass[a4paper]{ctexart}
\usepackage{geometry}
\usepackage{fontspec}
\setmainfont{Consolas}
\geometry{top=0.8in,bottom=1in,left=1.5cm,right=1.5cm}
\linespread{1.2}
\title{Nature's Call \textemdash \; Group Presentation}
\author{Group 5}
\begin{document}
\maketitle
\Large
\section{Opening}
Good morning, everyone!

Imagine waking up to a world where the air is fresh, the forests are lush, and the oceans teem with life.
Sadly, that world is slipping away as environmental problems like climate change,
pollution, and deforestation take their toll. Today, I'm here to talk about the environmental issues and how we can address them.
Together, we have the power to answer Nature's call before it's too late.

\section{Environmental Problems}
Environmental problems include climate change, pollution, deforestation, and biodiversity loss.
Currently, global temperatures are rising, plastic and air pollution persist, forests are shrinking,
and many species face extinction due to human activity.

\section{Address them!}
And here are ways to address these pressing issues.
\begin{itemize}
    \item Reduce emissions: Shift to renewable energy and improve energy efficiency.
    \item Cut pollution: Limit waste, promote recycling, and ban harmful chemicals.
    \item Protect nature: Enforce conservation laws and restore ecosystems.
    \item Promote awareness: Educate people on sustainable practices.
    \item Global cooperation: Implement international agreements like the Paris Accord.
\end{itemize}
And that's what nature is calling.
Not only does the call mean ``the power of nature to heal people'' but it also call on us to improve the poor situation.
We should answer the nature's call and take action in no time.

\section{Poster design introduction}
Now let me introduce our poster themed on ``Nature's Call''

The design concept of this poster centers around the theme of advocating for nature protection.

\subsection{background}
The background features a powerful contrast between the majestic
snow-covered mountains symbolizing the pristine beauty of nature,
and the black-and-white image of deforestation debris,
representing the destruction and degradation of the environment.

\subsection{top}
The text at the top, ``ANSWER NATURE'S CALL'',
serves as a strong call to action,
urging viewers to respond to the urgent needs of the environment.
The phrases ``SAVE THE PLANET'' and ``PRESERVE THE BEAUTY'' further emphasize the importance of environmental conservation.

\subsection{hashtags}
The use of hashtags like ``\#I'm here, but not forever'',
and others create a sense of urgency and personal connection,
implying that natural beauty is transient and needs immediate protection.

\subsection{title}
The title ``Nature's Call'' in bold,
black letters stands out prominently, reinforcing the central message.
The subtitle ``Answer With Action'' encourages viewers not just to be aware
but to take concrete steps towards environmental protection.

\subsection{final}
The final message at the bottom, ``The call of nature is louder than ever.
It's not just a plea; it's a demand for change. Together, we can turn the tide'',
sums up the poster's essence, highlighting the critical need for collective action to address environmental issues.

\section{Closing}
In conclusion, the call of nature is louder than ever. It's not just a plea;
it's a demand for change.
Each of us has a role to play—whether by reducing emissions, protecting nature, or promoting awareness. Let's not wait for someone else to act.
Together, we can turn the tide and preserve the beauty of our planet for generations to come.
Thank you!
\end{document}